HyperLogLog: Exponentially Bad in Adversarial Settings

### 2020-04-29 docs/HLL_exp_bad/main.tex
changes

We then challenge the adversary to pick the largest possible number of items to add to the sketch from our set of  7,311,616 possible inputs while trying to keep the cardinality estimate as low as possible, either in the S2 or the S4 scenario. As a second experiment, and in order to get results that can be directly compared to the work of~\cite{hllvuln}, we mounted our attack in their more restrictive setting: instead of picking from the universe of possible strings, the adversary has to choose what to insert from a set of 250,000 random items that are given to him. Finally, for completeness, we also run the attacks against HLL sketches that are initially empty. All attacks were run 30 times and the outcomes averaged. Our results are reported in Tables~\ref{table:tab1} and~\ref{table:tab2}, which detail the estimated cardinality at the beginning of the attack, the number of items added by the adversary, and the cardinality estimate after adding the adversary's items.

>>>>

We then challenge the adversary to pick the largest possible number of items to add to the sketch from our set of  7,311,616 possible inputs while trying to keep the cardinality estimate as low as possible, either in the S2 or the S4 scenario. As a second experiment, and in order to get results that can be directly compared to the work of~\cite{hllvuln}, we mounted our attack in their more restrictive setting: instead of picking from the universe of possible strings, the adversary has to choose what to insert from a set of 250,000 random items that are given to it. Finally, for completeness, we also run the attacks against HLL sketches that are initially empty. All attacks were run 30 times and the outcomes averaged. Our results are reported in Tables~\ref{table:tab1} and~\ref{table:tab2}, which detail the estimated cardinality at the beginning of the attack, the number of items added by the adversary, and the cardinality estimate after adding the adversary's items.
